### 2023-02-08 paper-thesis/chapters/10-coc.tex
First working compilation

In conventional dependently typed languages, evaluation is often done using De Bruijn indices, which use numbers to identify variables. However, we chose to use names rather than De Bruijn indices, because scope graphs work based on names. Using De Bruijn indices would also prevent us from using editor services that rely on \verb|.ref| annotations (which are Spoofax annotations that declare one name as being a use of another name that is a definition).

>>>>

In conventional dependently typed languages, evaluation is often done using De Bruijn indices.  De Bruijn representation~\cite[Section 6.1]{tapl} uses the distance from a binder to identify a variable. In this representation, alpha equivalence is the same as syntactic equivalence, which can simplify the manipulation of terms. However, we chose to use names rather than De Bruijn indices, because scope graphs work based on names. Using De Bruijn indices would also prevent us from using editor services that rely on \verb|.ref| annotations (which are Spoofax annotations that declare one name as being a use of another name that is a definition).
